SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-10-29 docs/questioning.tex
some changes

Figure~\ref{fig:defenses} presents a taxonomy of the
defenses that protect web applications against attacks based on
code injection vulnerabilities.
We can identify three main approaches, namely:
{\it design-based}, {\it behavior-based}
and {\it hybrid}.
The design-based category involves mechanisms that make applications
immune to different attack vectors by design~\cite{JL75,L81}.
The behavior-based incorporates a variety of methods and
schemes that inspect the behavior of applications
and detect attacks based on specific criteria~\cite{D76,A00}.
Both categories involve more than one subcategories.
The hybrid category borrows elements from more than one subcategories.
For every subcategory we provide elements regarding
every dimension described in Section~\ref{sec:dimensions}.

Table~\ref{tab:comp} groups the various subcategories
and for every mechanism provides the following:

@@

\subsubsection{Code Rewriting}

@@

The training subcategory, includes some mechanisms
that can be easily circumvented. For example,
consider an application that will send the password 
for a forgetful user via email by executing
the following query:
\bgroup
\lstset{language=SQL}
\begin{small}
\begin{lstlisting}
SELECT password from userdata WHERE id = 'Alice'
\end{lstlisting}
\end{small}
\egroup
\noindent
This same application could allow users to lock their terminal,
but allow the unlocking either with the user's password or with
the administrator password (the 4.3 {\sc bsd} {\em lock} command
behaved in this peculiar way).
The corresponding query to verify the password on the locked
workstation would be as follows:
\bgroup
\lstset{language=SQL}
\begin{small}
\begin{lstlisting}
SELECT password from userdata WHERE id = 'Alice' OR
id = 'admin'
\end{lstlisting}
\end{small}
\egroup
\noindent
A traditional {\sc sql} injection attack protection system like {\sc didafit},
could be easily escaped since a malicious user, could obtain the
administrator's password by email by entering on the password retrieval form
as his user identifier the following:
\bgroup
\lstset{language=SQL}
\begin{small}
\begin{lstlisting}
nosuchuser' OR id = 'admin
\end{lstlisting}
\end{small}
\egroup
\noindent
However, mechanisms that create signatures that involve
elements not only associated with the code statements
(i.e. {\sc amnesia} and {\sc sd}river)
could detect such attacks. Specifically,
{\sc sd}river associates a complete stack trace with the
root of an {\sc sql} statement, thus it can correlate
queries with their call sites and detect attacks
like the aforementioned one.
In a similar manner, training tools that detect
{\sc xss} attacks based on JavaScript injection
would fail to detect a mimicry attack like the
one mentioned in Subsubsection~\ref{sec:tree}.

@@

  \multirow{3}{*}{Parse-Tree Validation}

@@

>>>>

Figure~\ref{fig:defenses} presents a taxonomy of the
defenses that protect web applications against attacks based on
code injection vulnerabilities.
We can identify three main approaches, namely:
{\it design-based}, {\it behavior-based}
and {\it hybrid}.
The design-based category involves mechanisms that make applications
immune to different attack vectors by design~\cite{JL75,L81}.
The behavior-based incorporates a variety of methods and
schemes that inspect the behavior of applications
and detect attacks based on specific criteria~\cite{D76,A00}.
Hybrid mechanisms borrow characteristics from both categories.
Table~\ref{tab:comp} groups the various subcategories
and for every mechanism provides the following:

@@

@@

The training subcategory, includes some mechanisms
that can be easily circumvented. For example,
consider an application that will send the password 
for a forgetful user via email by executing
the following query:
\bgroup
\lstset{language=SQL}
\begin{small}
\begin{lstlisting}
SELECT password from userdata WHERE id = 'Alice'
\end{lstlisting}
\end{small}
\egroup
\noindent
This same application could allow users to lock their terminal,
but allow the unlocking either with the user's password or with
the administrator password (the 4.3 {\sc bsd} {\em lock} command
behaved in this peculiar way).
The corresponding query to verify the password on the locked
workstation would be as follows:
\bgroup
\lstset{language=SQL}
\begin{small}
\begin{lstlisting}
SELECT password from userdata WHERE id = 'Alice' OR
id = 'admin'
\end{lstlisting}
\end{small}
\egroup
\noindent
A traditional {\sc sql} injection attack protection system like {\sc didafit},
could be easily escaped since a malicious user, could obtain the
administrator's password by email by entering on the password retrieval form
as his user identifier the following:
\bgroup
\lstset{language=SQL}
\begin{small}
\begin{lstlisting}
nosuchuser' OR id = 'admin
\end{lstlisting}
\end{small}
\egroup
\noindent
However, mechanisms that create signatures that involve
elements not only associated with the code statements
(i.e. {\sc amnesia} and {\sc sd}river)
could detect such attacks. Specifically,
{\sc sd}river associates a complete stack trace with the
root of an {\sc sql} statement, thus it can correlate
queries with their call sites and detect attacks
like the aforementioned one.
In a similar manner, training tools that detect
{\sc xss} attacks based on JavaScript injection
would fail to detect a mimicry attack like the
one mentioned in Subsubsection {\sc tba}.

@@

@@

  \multirow{4}{*}{{\sc isr}}
